---
title: "PIPAH part 2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PIPAH_part2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  dev='png',
  fig.path="figures/")
```

```{r setup, include=F}
devtools::install_github("martinlaw/curtailment")
library(curtailment)
library(ggplot2)
```

## Simon design ##
```{r, echo=F}
simon <- find2stageDesigns(nmin=6,
                           nmax=14,
                           p0=0.05,
                           p1=0.3,
                           alpha=0.05,
                           power=0.8)

n14 <- singlearmDesign(nmin=14,
                           nmax=14,
                           C=2,
                           p0=0.05,
                           p1=0.3,
                           alpha=0.05,
                           power=0.8,
                           minstop=8,
                           minthetaE=0.9)

n14.stop10 <- singlearmDesign(nmin=14,
                           nmax=14,
                           C=2,
                           p0=0.05,
                           p1=0.3,
                           alpha=0.05,
                           power=0.8,
                           minstop=10,
                           minthetaE=0.9)

n15 <- singlearmDesign(nmin=15,
                       nmax=15,
                       C=3,
                       p0=0.05,
                       p1=0.3,
                       alpha=0.05,
                       power=0.8,
                       minstop=6,
                       minthetaE=0.9)
```


```{r simon.xmax34, fig.height=4, fig.width=6, warning=T, echo=F}
drawDiagram(simon, xmax=34, ymax=34)$diagram

```

## Selected SC designs ##

These designs have stochastic curtailment for futility and non-stochastic curtailment for benefit. This prevents the trial ending for benefit when the conditional power is relatively low, say approximately 0.85, and also means that any decision to stop for benefit is only taken when trial success would be guaranteed if the trial were to continue until the maximum sample size was reached.



```{r n14.4.xmax34, fig.height=4, fig.width=6, warning=T, echo=F}
drawDiagram(n14, xmax=34, ymax=34)$diagram
```

```{r n14.3.xmax34, fig.height=4, fig.width=6, warning=T, echo=F}
drawDiagram(n14.stop10, xmax=34, ymax=34)$diagram
```

```{r n15.xmax34, fig.height=4, fig.width=6, warning=T, echo=F}
drawDiagram(n15, xmax=34, ymax=34)$diagram

```

